An introduction to lightlabsFDS

### 2012-02-29 presentations/lightlabsFDS_mar-2012/pres.tex
Updated presentation a little.

\documentclass[landscape]{foils}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[pdf]{pstricks}
\input defs.tex
\raggedright
\special{! TeXDict begin /landplus90{true}store end }
\renewcommand{\oursection}[1]{
\foilhead[-1.0cm]{#1}
}

@@

\oursection{Example: time-domain solver}

\psset{unit=1.5cm}
\psset{gridcolor=green, subgridcolor=yellow}
\begin{center}
\begin{pspicture}(8,5)
    \let\psgrid\relax

    \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (1,2.2)(4,2.8)
    \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (3,1)(5,4)
    \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (4,1.4)(7,2)
    \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (4,3.0)(7,3.6)
    \rput[B](4,4.1){Device}
    \psline[linestyle=dashed](1.6,0.6)(1.6,4.0)
    \rput[B](1.6,4.1){in}
    \psline[linestyle=dashed](6.4,0.6)(6.4,4.0)
    \rput[B](6.4,4.1){out}
\end{pspicture}
\end{center}
Time-domain issues include
\BIT
\I  Input: clean excitation at input requires an auxiliary simulation
\I  Device: approximations required for material dispersion
\I  Output: overlap integrals must be repeatedly calculated 
        \emph{during} the simulation
\EIT
\newpage

\begin{center}
\begin{pspicture}(8,5)
    \psgrid

    \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (1,2.2)(4,2.8)
    \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (3,1)(5,4)
    \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (4,1.4)(7,2)
    \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (4,3.0)(7,3.6)
    \rput[B](4,4.1){Device}
    \psline[linestyle=dashed](1.6,0.6)(1.6,4.0)
    \rput[B](1.6,4.1){in}
    \psline[linestyle=dashed](6.4,0.6)(6.4,4.0)
    \rput[B](6.4,4.1){out}
\end{pspicture}
\end{center}
\end{document}

>>>>

\documentclass[landscape]{foils}
\usepackage{graphicx}
\usepackage{amsmath}
% \usepackage[pdf]{pstricks}
\input defs.tex
\raggedright
\special{! TeXDict begin /landplus90{true}store end }
\renewcommand{\oursection}[1]{
\foilhead[-1.0cm]{#1}
}

@@

\oursection{Example}

% \psset{unit=1.5cm}
% \psset{gridcolor=green, subgridcolor=yellow}
% \begin{center}
% \begin{pspicture}(8,5)
%     \let\psgrid\relax
% 
%     \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (1,2.2)(4,2.8)
%     \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (3,1)(5,4)
%     \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (4,1.4)(7,2)
%     \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (4,3.0)(7,3.6)
%     \rput[B](4,4.1){Device}
%     \psline[linestyle=dashed](1.6,0.6)(1.6,4.0)
%     \rput[B](1.6,4.1){in}
%     \psline[linestyle=dashed](6.4,0.6)(6.4,4.0)
%     \rput[B](6.4,4.1){out}
% \end{pspicture}
% \end{center}
Time-domain issues include
\BIT
\I  Input: clean excitation at input requires an auxiliary simulation
\I  Device: approximations required for material dispersion
\I  Output: overlap integrals must be repeatedly calculated 
        \emph{during} the simulation
\EIT
\newpage

% \begin{center}
% \begin{pspicture}(8,5)
%     \psgrid
% 
%     \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (1,2.2)(4,2.8)
%     \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (3,1)(5,4)
%     \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (4,1.4)(7,2)
%     \psframe*[linecolor=gray, fillcolor=gray, fillstyle=solid] (4,3.0)(7,3.6)
%     \rput[B](4,4.1){Device}
%     \psline[linestyle=dashed](1.6,0.6)(1.6,4.0)
%     \rput[B](1.6,4.1){in}
%     \psline[linestyle=dashed](6.4,0.6)(6.4,4.0)
%     \rput[B](6.4,4.1){out}
% \end{pspicture}
% \end{center}
\BIT
\I  Fundamental problem: trying to use a time-domain solver as a 
        frequency-domain solver.
\I  Additionally, no method to measure simulation error!
\EIT
\newpage

\BIT
\I  Allow direct access to frequency-domain data.
\I  Take care of input and output fields outside of the simulation.
\I  Material dispersion explicitly defined.
\I  Simulation error well defined.
\EIT
\newpage

\BIT
\I  Frequency-domain solver made possible by correct choice of PML and 
        linear algebra algorithm.
\I  See: Wonseok Shin, Shanhui Fan, 
            ``Choice of the perfectly matched layer boundary condition for 
            frequency-domain Maxwell's equations solvers'',
            Journal of Computational Physics (January 2012).
\EIT

\oursection{Interface}
\BIT
\I  No installation required.
\begin{verbatim}
>>> [E, H] = fds(omega, epsilon, J); % Run FDS.
\end{verbatim}
\EIT
\end{document}
